Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-11-15 ms/main.tex
A
faculty added

\affil[1]{School of Computer Science, Interdisciplinary Center Herzliya, Herzliya, Israel}
\affil[2]{School of Plant Sciences and Food Security, Tel Aviv University, Tel Aviv, Israel}
\affil[3]{Department of Biology, Stanford University, Stanford, CA}
\affil[4]{School of Zoology, Tel Aviv University, Tel Aviv, Israel}
\affil[5]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv, Israel}
\affil[*]{Corresponding author: yoav@yoavram.com}

>>>>

\affil[1]{School of Computer Science, Interdisciplinary Center Herzliya, Herzliya, Israel}
\affil[2]{School of Plant Sciences and Food Security, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
\affil[3]{Department of Biology, Stanford University, Stanford, CA}
\affil[4]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
\affil[5]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv, Israel}
\affil[*]{Corresponding author: yoav@yoavram.com}
